Shannon-Inspired Information in the Clinical Use of Neural Signals Concerning Post-Comatose Patients

### 2023-02-01 ART_Noh/Noh.tex
Mscislawski article added

\paragraph{Acknowledgments}
I~thank an anonymous reviewer for this journal for comments that prompted important clarifications in the penultimate draft. I~am also deeply grateful to Carrie Figdor for constructive feedback on a~previous draft.\\
This work was supported by a research promotion program of SCNU.

>>>>

\paragraph{Acknowledgments.}
I~thank an anonymous reviewer for this journal for comments that prompted important clarifications in the penultimate draft. I~am also deeply grateful to Carrie Figdor for constructive feedback on a~previous draft.\\
This work was supported by a research promotion program of SCNU.
